Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
small editing intro

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on a counterexample
guided inductive synthesis (CEGIS)~\cite{sketch} loop.
The first approach uses a naive
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon and, subsequently, verifies its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.
As it requires explicit unfolding up to a completeness
threshold, this approach may result in a state space explosion.
Instead of explicitly unfolding the dynamics, the second approach 
employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously.
Additionally, the second approach uses
abstraction refinement enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.

>>>>

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
The first approach uses a naive
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.
As it requires explicit unfolding up to a completeness
threshold, this approach may result in a state space explosion.
Instead of explicitly unfolding the dynamics, the second approach 
employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously.
Additionally, the second approach uses
abstraction refinement enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.
